Introduction

### 2012-10-25 dissertation/tmpsolutions.tex
conclusions
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@413 43ef1190-90fd-4dd7-a769-d0121f02b80e

>>>>

\subsection{Conclusion}

These are my current opinions:

At present, I feel the best way to progress is to publish a paper on
VoID extensions as well as fully indexed stores in a conditional
regime. I should do some work to get the notation and theory well
founded, but defer \SRL{} for later.

The 3.~semester evaluation committee also critisized the lack of a
paper, and said that I should produce a paper, at least a draft before
the end of the year. If I embark on a study of \SRL{}, this would not
be possible.

The study of \SRL{} is very interesting, so I should look into that
once the first paper has been published, but possibly seek partners or
an external resource.

Amongst the below references, the most important are
\cite{selectivityPRM}, \cite{Lin:2011:LRB:2063016.2063042} and
\cite{splendid}.
